DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-09-05 manuscript/manuscript.Rmd
reoder sections

# Neural architecture for loss reserving

As shown in Figure \ref{fig:dt}, DeepTriangle is a multi-task network with two prediction goals: claims outstanding and paid loss. We construct one model for each line of business and each model is trained on data from multiple companies.

## Training Data

@@

@@

DeepTriangle utilizes a sequence-to-sequence architecture inspired by @sutskever2014sequence and @DBLP:journals/corr/SrivastavaMS15.

@@

## Data

We validate the modeling approach on data from National Association of Insurance Commissioners (NAIC) Schedule P triangles [@meyers2011loss]. The dataset corresponds to claims from accident years 1988-1997, with development experience of 10 years for each accident year.

We use the following variables from the dataset in our study: line of business, company code, accident year, development lag, incurred loss, cumulative paid loss, and net earned premium. Claims outstanding, for the purpose of this study, is derived as incurred loss less cumulative paid loss.

We use data as of year end 1997 for training, and evaluate predictive performance on the development year 10 ultimates.

>>>>

# Data and model architecture

In this section, we discuss the dataset used for our experiments and the proposed model architecture.

## Data source

We use the National Association of Insurance Commissioners (NAIC) Schedule P triangles [@meyers2011loss]. The dataset corresponds to claims from accident years 1988-1997, with development experience of 10 years for each accident year. In Schedule P data, the data is aggregated into accident year-development year records.

We use the following variables from the dataset in our study: line of business, company code, accident year, development lag, incurred loss, cumulative paid loss, and net earned premium. Claims outstanding, for the purpose of this study, is derived as incurred loss less cumulative paid loss. The company code is a categorical variable that denotes which insurer the records are associated with.

## Training/testing setup

@@

In our case, data as of year end 1997 is used for training. WE then evaluate predictive performance on the development year 10 cumulative paid losses.

@@

As shown in Figure \ref{fig:dt}, DeepTriangle is a multi-task network utilizing a sequence-to-sequence architecture [@sutskever2014sequence; @DBLP:journals/corr/SrivastavaMS15] with two prediction goals: claims outstanding and paid loss. We construct one model for each line of business and each model is trained on data from multiple companies.

@@
